Verifying Demonstrations

### 2017-07-24 intro.tex
Works through text and slides
Privacy section not work through entirely yet.
Adds useful quotes to intro

@@

>>>>

\blockcquote{2016DemonstrationsInSeoul}{%
  The rallies stretch from midday to late night --- some people stay for 
  several hours, others just several minutes.%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  The demonstrators not only gather in open space, but also small alleys and 
  between buildings.%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  For the police, the aim is to measure the maximum crowd occupying a certain 
  space at any given time so that they could determine the size of police 
  personnel and resources to deploy%
}

\blockcquote{2016DemonstrationsInSeoul}{%
  Organizers seek to track the entire flow of people from the protest’s start 
  to its finish. They collect estimates given by counters deployed at different 
  locations to size up the crowds in each area and update the numbers 
  throughout the duration of the protest.%
}

\blockcquote{HowToEstimateCrowdSize}{%
  the more widely that a crowd is spread out, the more challenging it can be to 
  get an accurate estimate of those attending, as it can become difficult to 
  determine whether people near the event's perimeter are there for the event 
  or are in the area for other reasons,%
}

@@

%In the case of the Korean demonstrations~\cite{2016DemonstrationsInSeoul}, this 
%was in one place during an entire day and then repeated for several weekends.
%In the case of the Women's Marches in the US~\cite{2017WomensMarchesInUS}, they
%were in several locations at the same time.

\blockcquote{HowToEstimateCrowdSize}{%
  Crowd size is also needed for media news reports and to historically record 
  the event%
}
